Data organization in spreadsheets

### 2018-03-12 manuscript.Rmd
Mention K. Briney's idea of dates as YYYYMMMDD
Fix complex expression, "than that which is" → "than data"

Another way to force Excel to treat dates as text is to begin the date with an
apostrophe, like this: `'2014-06-14`
(see <http://bit.ly/twitter_apos>). Excel will treat the
cells as text, but the apostrophe will not appear when you view the spreadsheet
or export it to other formats. This is a handy trick, but it requires impeccable
diligence and consistency.

Alternatively, you could
create three separate columns
with year, month, and day. Those will be ordinary numbers, and so
Excel won't mess them up.

@@

For example, in Figure 10A, a suspicious entry is highlighted. It would be
better to include an additional column that indicates the outliers (as in Figure
10B). The highlighting is nice visually, but it is hard to extract that
information for use in the later analysis. Analysis programs can much more
readily handle data that are stored in a column than that which is encoded in
cell highlighting, font, etc. (and in fact this markup will be lost completely
in many programs).

>>>>

Another way to force Excel to treat dates as text is to begin the date with an
apostrophe, like this: `'2014-06-14`
(see <http://bit.ly/twitter_apos>). Excel will treat the
cells as text, but the apostrophe will not appear when you view the spreadsheet
or export it to other formats. This is a handy trick, but it requires impeccable
diligence and consistency.
Alternatively, you could
create three separate columns
with year, month, and day. Those will be ordinary numbers, and so
Excel won't mess them up.
Finally, you could represent dates as an 8-digit integer of the form
`YYYYMMDD`, for example `20140614` for `2014-06-14` [see @briney2017].

@@

For example, in Figure 10A, a suspicious entry is highlighted. It would be
better to include an additional column that indicates the outliers (as in Figure
10B). The highlighting is nice visually, but it is hard to extract that
information for use in the later analysis. Analysis programs can much more
readily handle data that are stored in a column than data encoded in
cell highlighting, font, etc. (and in fact this markup will be lost completely
in many programs).
